---
title: "Reproducible Workflow for Exploring Pleiotropic Associations in GWAS Summary Statistics"
author: "Christina Y. Feng, Pierre Emmanuel Sugier, Nan Zou, and Benoit Liquet"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

### Overview

This vignette provides a reproducible workflow accompanying the tutorial,
*A Guide for Exploring Pleiotropic Associations in Genome-Wide Association Studies using Summary Statistics*.

The workflow uses summary statistics from breast cancer and thyroid cancer
examples. No individual-level data are provided.

### Required packages

```{r setup, message=FALSE, warning=FALSE}
source("../R/00_setup.R")
```

### Load and prepare summary statistics

```{r prepare-data}
source("../R/01_prepare_data.R")
```

### ASSET analysis

```{r asset}
source("../R/02_asset.R")
```

### PLACO analysis

```{r placo}
source("../R/03_placo.R")
```

### GPA analysis

```{r gpa}
source("../R/04_gpa.R")
```

### CPBayes analysis

```{r cpbayes}
source("../R/05_cpbayes.R")
```

### GCPBayes gene-level analysis

```{r gcpbayes}
source("../R/06_gcpbayes.R")
```

### Summary of outputs

The workflow saves method-specific results in the `results/` folder:

- `prepared_summary_statistics.rds`
- `asset_results.rds`
- `placo_results.rds`
- `gpa_results.rds`
- `cpbayes_results.rds`
- `gcpbayes_results.rds`

### Session information

```{r session-info}
sessionInfo()
```
